Make any stupid plot you want

### 2020-12-22 draft/sections/math.tex
more p

In this section we will define the artist as a mapping from the sheaf $O(E)$ representing the data to a pre-render space $O(H)$. 
\begin{equation}
    A: \mathcal{O}(E) \rightarrow \mathcal{O}(H)
\end{equation}
The artist decomposes to data $E$ to visual mappings $V$ and $V$ mappings composited to a visual in prerender space $H$. In order to define $A$, we first define the visual fiber bundle $V$ that shares basespace $K$ with $E$ as ($V$,$K$, $\pi$, $P$) with section $\mu: V \rightarrow K$. The fiber $P$ is the space of visual variables $\mu$ \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels} that can be encoded in the visualization being generated by $A$.

\subsubsection{Example}
If for example, a line artist as defined in \cite{Matplotlib} only supported the visual mappings xposition, yposition, width, color, style; then the $P$ for this line artist would be:
\begin{itemize}
    \item $C = \{\text{xposition, yposition, linewidth, color, linestyle}\}$ 
    \item $DT =\{\mathbb{R}, \mathbb{R}, \mathbb{R}, \mathbb{R}^3, f\}$ 
    \item $\sigma: C \rightarrow DT$ 
    \item $P = \Gamma(\sigma) = \Gamma(\mu)$ 
\end{itemize}

\subsubsection{Visual Channels}

The function $\nu: E \rightarrow V$ is a mapping from the data bundle to the visual bundle 
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi"'] \arrow[r, "\nu"] & V \arrow[ld, "\pi"'] \\
        K                                    &                     
        \end{tikzcd}
\end{equation}

@@

\subsubsection{Pipeline}
The full visualization path is
\begin{equation} 
    \begin{tikzcd}
        E \arrow[r, "\nu=transforms"] & V                                                              & \xi^*V \arrow[r, "Q = \text{set attrs}"]                             & H \\
                                  & K \arrow[lu, "\tau = data"] \arrow[u, "{\mu = \{\tau,\nu\}}"'] & S \arrow[l, "\xi - init?draw"] \arrow[u, "\xi^*\mu = \nu\circ\tau"'] &  
    \end{tikzcd}
\end{equation}

>>>>

In this section we will define the artist as a mapping from a sheaf $\mathcal{O}(E)$  to $\mathcal{O}(H)$. 
\begin{equation}
    A: \mathcal{O}(E) \rightarrow \mathcal{O}(H)
\end{equation}
The artist decomposes to data $E$ to visual mappings $V$ and $V$ mappings pulled back along $\xi$ to $\xi^*V$ which is then composited to a visual in prerender space $H$.

\begin{equation}
    \label{eq:artist}
\begin{tikzcd}
    E \arrow[r, "\nu"] \arrow[rd, "\pi"'] & V \arrow[d, "\pi"] & \xi^*V \arrow[r, "Q"] \arrow[d, "\xi^*\pi"'] & H \arrow[ld, "\pi"] \\
                                          & K                  & S \arrow[l, "\xi"']                          &                    
\end{tikzcd}
\end{equation}

The visual fiber bundle ($V$, $K$, $\pi$, $P$) has section $\mu: V \rightarrow K$ that resolves to a visual variable $\mu$ \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels} in fiber $P$. The space of visual variables types in $P$ is restricted to the types $Q$ takes as input.

\subsubsection{Example} 
Given a  $Q$ that manufactored lines with signature $Q(\mu_{xpos}, \mu_{ypos}, \mu_{width}, \mu_{color}, \mu_{style})$ then the $P=\Gamma(\mu)$ for this line artist would be:
\begin{itemize}
    \item $C = \{\text{xpos, ypos, width, color, style}\}$ 
    \item $DT =\{\mathbb{R}, \mathbb{R}, \mathbb{R}, \mathbb{R}^3, f:s\mapsto\mathbb{R}^3 \}$ 
    \item $P = U \times_{DT} C$
\end{itemize}

\subsubsection{Visual Channels}
The function $\nu: E \rightarrow V$ is a mapping from the data bundle to the visual bundle 
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi"'] \arrow[r, "\nu"] & V \arrow[ld, "\pi"'] \\
        K                                    &                     
        \end{tikzcd}
\end{equation}

@@
